\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-12-03 tex/gitlinks.tex
ufff; wrote inclination section

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/56f89997cccb24bacd2c3b8d1b6d990961902783/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/56f89997cccb24bacd2c3b8d1b6d990961902783/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/56f89997cccb24bacd2c3b8d1b6d990961902783/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/3fb4d04da2b805c28ab3df4b1bdaf4ee4c772c8c/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/3fb4d04da2b805c28ab3df4b1bdaf4ee4c772c8c/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/3fb4d04da2b805c28ab3df4b1bdaf4ee4c772c8c/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}
